Uniform sampling across the whole territory without any cells

### 2024-08-30 First_steps/No_tree_no_grid.Rmd
RB instead of RPD

# Table for comparison
diff_var <- data.frame(`Difference between totals` = paste0(round(mapply(function(x,y){unlist(100*(max(x,y)-min(x,y))/min(x, y))}, unlist(THEO_df[1]), unlist(RES_df[1])), digits = 3), "%"), `Difference between variances` = paste0(round(mapply(function(x,y){100*(max(x,y)-min(x,y))/min(x,y)}, unlist(THEO_df[2]), unlist(RES_df[2])), digits = 3), "%") )
# diff_var <- ifelse(diff_var == "NaN%", 0, diff_var)
diff_var[diff_var == "NaN%"] <- "0%"
```

>>>>

# Table for comparison
diff_var <- data.frame(`Difference between totals` = paste0(round(mapply(function(x,y){unlist(100*(y-x)/x)}, unlist(THEO_df[1]), unlist(RES_df[1])), digits = 3), "%"), `Difference between variances` = paste0(round(mapply(function(x,y){unlist(100*(y-x)/x)}, unlist(THEO_df[2]), unlist(RES_df[2])), digits = 3), "%") )
# diff_var <- ifelse(diff_var == "NaN%", 0, diff_var)
diff_var[diff_var == "NaN%"] <- "0%"
```
